Objective-First Nanophotonic Design Plan

### 2012-09-21 plan/plan.tex
Added figure.

\documentclass{book}
\usepackage{amsmath}
% \usepackage{hyperref}

@@

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the following relationship,
    \E  {bi-affine property}
        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
    which will prove to be very useful.

@@

\subsection{optimality condition}

\section{General strategy to solve the problem}
\subsection{Field update}
Give the \emph{specific} interfaces here. 
What exactly gets input and what does each update output?
\subsection{Structure update}

>>>>

\documentclass{book}
\usepackage{amsmath}
% \usepackage{hyperref}
\usepackage{pstricks}

@@

\subsection{Bi-affine property of the physics residual}
Critically, \eq{wave equation in E} is not only linear in $E$,
    but is also affine in $\epsilon$.
This allows us to form the extremely useful relationship,
    \E  {bi-affine property}
        {A_i(z)x_i - b_i(z) = B(x_i)z - d(x_i) = 0,}
    where $B(x_i) \in \comps^{n \times n}$ and $d(x_i) \in \comps^n$.

@@

\subsection{Optimality condition}
Based on the problem definition in \eq{rigorous problem statement},
    we can write down a set of equations that, when met,
    signal that we have arrived at a locally optimal point.
Otherwise known as the Karush-Kuhn-Tucker (KKT) conditions, % Ref boyd
    these are, for \eq{rigorous problem statement},
    \EE {KKT conditions} % Check how these work out for complex values!!!
        {|c_{ij}\T x_i| - \beta_{ij} &\le 0, \\
        \alpha_{ij} - |c_{ij}\T x_i| &\le 0, \\
        A_i(z)x_i - b_i(z) &= 0, \\
%         % Lambda dual variables not needed because they do not appear 
%         % in the last KKT condition.
%         \lambda_{\alpha ij} &\ge 0, \\ 
%         \lambda_{\beta ij} &\ge 0, \\
%         \lambda_{\alpha ij}(|c_{ij}\T x_i| - \beta_{ij}) &= 0, \\
%         \lambda_{\beta ij}(\alpha_{ij} - |c_{ij}\T x_i|) &= 0, \\
        \nabla_z g(z) + \sum_i B(x_i)\T \nu_i &= 0,
        }
    where $\nu_i \in \comps^n$ are dual variables.

\section{General strategy to solve the problem}

\begin{pspicture}(6,5)(-6,-2)
\psset{gridcolor=green, subgridcolor=yellow}
    \let\psgrid\relax

    % Paradigm
    \rput(0,4.3){optimization paradigm}
    \psline(-2.2,4)(2.2,4) % top
    \psline(-2.2,4)(-2.2,2) % left
    \psline(2.2,4)(2.2,2) % right
    \psline(-2.2,2)(-1,2)
    \psline(2.2,2)(1,2)
    \psline(-1,2.2)(1,2.2)
    \psline(-1,2)(-1,2.2)
    \psline(1,2)(1,2.2)

    % Parameterization
    \psframe(-.8,0.8)(.8,-0.4) 
    \rput(0,-0.7){\parbox{5cm}{\center structure\\ parameterization}}

    % Arrows
    \rput[r](-1.9,0.8){into sp}
    \psline(-1.6,1.8)(-1.6,0.2)
    \psline{->}(-1.6,0.2)(-1,0.2)

    \rput[l](1.9,0.8){out of sp}
    \psline(1.6,0.2)(1,0.2)
    \psline{<-}(1.6,1.8)(1.6,0.2)

    \rput[r](-4.3,3){initial input}
    \psline{->}(-4,3)(-2.4,3)

    \rput[l](4.3,3){output}
    \psline{<-}(4,3)(2.4,3)
\end{pspicture}

\subsection{Field update}
Give the \emph{specific} interfaces here. 
What exactly gets input and what does each update output?
\subsection{Structure update}
